Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-20 Paper/paper.tex
Starting to work on writing the theorem

\item If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$ then $f_{\NH}(k)$ is a non-decreasing function in $k$.
\item If $\lambda_{\RG}^{(l,l)}\leq \lambda_{\RG}^{(h,l)}$ and $\lambda_{\RG}^{(l,h)}\leq \lambda_{\RG}^{(h,h)}$ then $f_{\RG}(k)$ is a non-decreasing function in $k$.

>>>>

\item If $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)},\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ then $f_{\NH}(k)$ is a non-decreasing function in $k$.
\item If $\lambda_{\RG}^{(l,h)}\leq \lambda_{\RG}^{(h,h)},\lambda_{\RG}^{(l,l)}\leq \lambda_{\RG}^{(h,l)}$ then $f_{\RG}(k)$ is a non-decreasing function in $k$.
